\chapter{Feature Survey} \label{app:survey}

Imagine the most convenient way to work with (coding) assignments in a role of student (aka solver), professor or TA (aka instructors). Following is a list of features that you may or may not consider necessary. Every step is optional. With 5-10 seconds per feature, this form should take 7 minutes. The overall question -- How necessary is the given feature?

\begin{itemize}
\item
  Gain real developer experience using industry standard tools and best practices, i.e.~not a proprietary course-specific or university-specific environment.
\end{itemize}

\section{Solver -- Viewing \& Participation}\label{sec:solver-viewing-participation}

How important are the following features for solvers, ergo students?

\begin{itemize}
\item
  View course items and course announcements, e.g.~materials, links, tools, files.
\item
  Participate in discussions both privately or publicly, e.g.~over an assignment or course syllabus or materials.
\item
  Get notifications about important events, e.g.~new issue, update or post.
\item
  Customize notification type per event, e.g.~by an email or an in-app badges.
\item
  Use live audio / video / text chat, e.g.~to gain real-time support.
\item
  Search within the project's files, e.g.~by a folder or a file name or a file content.
\item
  Link to anything persistently, e.g.~to a specific file or its part, modification, history, issue or task.
\end{itemize}

\section{Solver -- Working on Assignments}\label{sec:solver-working-on-assignments}

How important are the following features for solvers, ergo students?

\begin{itemize}
\item
  View change history of an assignment solution, e.g.~show all modifications done to a specific file.
\item
  Work on solutions both online or locally, i.e.~choose preferred tool according to the specific task.
\item
  Take tests and quizzes (next to assignments), i.e.~fill up answers, code a little script or algorithm within a time period.
\item
  Participate in competitions, e.g.~continuously publishing results to show how everybody is doing.
\item
  Use various devices to work on assignments interchangeably, e.g.~class computer, laptop, home computer or even a smartphone (!!).
\item
  Use various editors to work on assignments interchangeably, e.g.~Eclipse, VS Code, Vim, Sublime, Gedit or even a browser (!!).
\item
  Obtain a reliable and persistent support, i.e.~create a traceable issue with discussion.
\item
  Use tagging (labeling) to mark or filter issues, e.g.~assignments, bonus questions, errors, bugs, suggestion.
\end{itemize}

\section{Solver -- Distribution}\label{sec:solver-distribution}

How important are the following features for solvers, ergo students?

\begin{itemize}
\item
  Synchronize local storage with the online storage on demand easily, i.e.~decide when the solution gets pushed to the server.
\item
  View and accept when the assignment gets updated by an instructor, e.g.~instructions, code base or testing scripts.
\item
  Submit solution legally even past due, i.e.~finish the assignment and ask for forgiveness later.
\item
  Verify solution submission in real time, i.e.~check if the solution is visible to the server and compiles.
\item
  Provide full-fledged REST API, i.e.~to integrate own scripts or third party IDE such as Eclips.
\end{itemize}

\section{Solver -- Evaluation}\label{sec:solver-evaluation}

How important are the following features for solvers, ergo students?

\begin{itemize}
\item
  Evaluate solutions online automatically in real-time, i.e.~show how many tests are passing and access log files.
\item
  Evaluate solutions locally on demand, i.e.~run testing scripts manually and explore results.
\item
  View testing scripts, i.e.~display the implementation of testing scripts.
\item
  Resubmit a solution legally, i.e.~trace when and what has been changed.
\end{itemize}

\section{Instructor -- Viewing \& Tracking}\label{sec:instructor-viewing-tracking}

How important are the following features for instructors, ergo professors and TAs?

\begin{itemize}
\item
  View individual solution modifications, e.g.~compare solutions to the assignment or to the working solution.
\item
  Track solution progress in time, e.g.~collect and evaluate towards or passed a due date.
\item
  Compare individual solutions to each other, e.g.~show differences between selected solutions.
\item
  Access full change history of individual solutions, e.g.~to show when and how often modifications were made.
\item
  Download all solutions at once including their full change history, i.e.~have complete solutions available locally.
\end{itemize}

\section{Instructor -- Evaluation}\label{sec:instructor-evaluation}

How important are the following features for instructors, ergo professors and TAs?

\begin{itemize}
\item
  Explore and evaluate individual solutions manually, e.g.~download and run in various editors or environments.
\item
  Collect all evaluations and summary, i.e.~evaluate all solutions at once gaining individual log files.
\item
  Collect and evaluate all solutions retrospectively to any point in history, e.g.~towards or n days pass the due date, or the most current versions.
\end{itemize}

\section{Instructor -- Integration \& Support}\label{sec:instructor-integration-support}

How important are the following features for instructors, ergo professors and TAs?

\begin{itemize}
\item
  Import user names, e.g.~directly from a learning management system.
\item
  Export collective evaluation output summary, e.g.~into a score sheet or directly to a learning management system.
\item
  Provide platform independence, e.g.~run GitLab including own internal instance, GitHub or other platforms.
\item
  Provide (remote) support to solvers in a standard traceable way, i.e.~without screen sharing or operating their computers.
\item
  Introduce linting to support solvers automatically, e.g.~syntax, format or coding style checkers.
\end{itemize}

\section{Instructor -- Creating Assignments}\label{sec:instructor-creating-assignments}

How important are the following features for instructors, ergo professors and TAs?

\begin{itemize}
\item
  Use templates to easily configure the basic environment, e.g.~in form of examples in documentation or self-standing tutorials.
\item
  Integrate external environments, e.g.~Google Collab, Overleaf, WolframAlpha.
\item
  Support coding assignments in an unlimited scope, e.g.~from simple text and short coding blocks to complex programming.
\item
  Support adding various languages and syntax, e.g.~Python, Perl, LaTeX, \\ HTML/CSS/JS, NodeJS, Markdown, Bash.
\item
  Support group assignments with selected solvers in charge, e.g.~set up a maintainer and set of developers per assignment.
\end{itemize}

\section{Instructor -- Distribution}\label{sec:instructor-distribution}

How important are the following features for instructors, ergo professors and TAs?

\begin{itemize}
\item
  Maintain a relation between assignments and their original working projects, i.e.~for parallel updating or cross-semester asignment modifications.
\item
  Allow multiple independent assignment versions, e.g.~to prevent cross-semester solution sharing.
\item
  Register students for an assignment by a CSV file, e.g.~an export from a learning management system.
\item
  Register students for an assignment using API, e.g.~using a learning management system's API.
\item
  Register students for an assignment manually, e.g.~to add specific solvers, such as the creator or TAs.
\end{itemize}

\section{Instructor -- Scoring}\label{sec:instructor-scoring}

How important are the following features for instructors, ergo professors and TAs?

\begin{itemize}
\item
  Allow variable scoring based on testing results, i.e.~different tasks may have different importance.
\item
  Adjust score based on early/late delivery, e.g.~percentage bonus or penalty around a due date.
\item
  Measure solutions similarities between each other, i.e.~plagiarism check across current or even passed semesters.
\item
  Additional (hidden) testing, e.g.~to prevent obscure trivial solutions.
\end{itemize}

\section{Comments \& Participation}\label{sec:comments-participation}

Thank you! Additionally you may indicate your experience and leave a comment. State your email address if you want to stay in touch or participate.

\begin{itemize}
\item
  Your recent roles
\item
  Your name
\item
  Your email address
\item
  Your experience, ideas, suggestions, comments
\end{itemize}
